Testing Charts: viewer's perceptual accuracy in surveys

### 2023-07-20 SDSS-2023/testing-charts-accuracy.qmd
shorten levels for income and education

@@

```{r}
#| label: fig-demographics
#| fig-cap: "Panelist's demographics matter, particularly, when the task difficulty increases. For aligned tiles, gender, age, and education are not significant factors. However, income levels do have - a small - effect. When income levels increase, the percentage of wrong answers (orange) decreases, while the percentage of correct answers (blue) increases slightly (significant at below 0.05). The more difficult task of comparing unaligned tiles, demographics are more significant.  XXX With increasing levels in education, we see a small drop in correct answers, as well as a small drop in wrong answers, for a significant increase in 'they are the same'."
#| fig-subcap: 
#|   - Comparisons of aligned tiles
#|   - Comparisons of unaligned tiles
#| fig-height: 5
#| fig-width: 7
#| layout-nrow: 2
#| out-width: 100%

>>>>

levels(round_123$educ5) <- c("Less than HS", "HS or equivalent", "Some college", "Bachelor", "Post graduate")

levels(round_123$income4) <- c("< $30k", "$30k - $60k", "$60k - $100k", "more than $100k")

@@

```{r}
#| label: fig-demographics
#| fig-cap: "Panelist's demographics matter, particularly, when the task difficulty increases. For aligned tiles, gender, age, and education are not significant factors. However, income levels do have - a small - effect. When income levels increase, the percentage of wrong answers (orange) decreases, while the percentage of correct answers (blue) increases slightly (significant at below 0.05). The more difficult task of comparing unaligned tiles, demographics are more significant.  XXX With increasing levels in education, we see a small drop in correct answers, as well as a small drop in wrong answers, for a significant increase in 'they are the same'."
#| fig-subcap: 
#|   - Comparisons of aligned tiles
#|   - Comparisons of unaligned tiles
#| fig-height: 4
#| fig-width: 7
#| layout-nrow: 2
#| out-width: 100%
